The Cluster Difference Imaging Photometric Survey (CDIPS). I. Light Curves \& Planet Candidates in Open Clusters from TESS Sectors 6 \& 7

### 2019-06-20 paper/ms.tex
paper words

% BEGIN NUMBERS
\newcommand{\numberpcs}{42\ }
\newcommand{\numberlcs}{99{,}999\ }
\newcommand{\numberclusters}{XXX\ }

% BEGIN CLUSTER TABLE
%FIXME: write code that will write these values
\newcommand{\cgXVIIInstartot}{}
\newcommand{\cgXVIIInstarcdipsI}{}
\newcommand{\gaiaXVIIInstartot}{}
\newcommand{\gaiaXVIIInstarcdipsI}{}

\newcommand{\kXIIInstartot}{}
\newcommand{\kXIIInstarcdipsI}{}
\newcommand{\dXIVnstartot}{}
\newcommand{\dXIVnstarcdipsI}{}
\newcommand{\bellXVIInstartot}{}
\newcommand{\bellXVIInstarcdipsI}{}
\newcommand{\banyanXIIInstartot}{}
\newcommand{\banyanXIIInstarcdipsI}{}
\newcommand{\banyanXIInstartot}{}
\newcommand{\banyanXIInstarcdipsI}{}
\newcommand{\banyanXInstartot}{}
\newcommand{\banyanXInstarcdipsI}{}
\newcommand{\krausXIVnstartot}{}
\newcommand{\krausXIVnstarcdipsI}{}
\newcommand{\ohXVIInstartot}{}
\newcommand{\ohXVIInstarcdipsI}{}
\newcommand{\rizzutoXInstartot}{}
\newcommand{\rizzutoXInstarcdipsI}{}
\newcommand{\roserXInstartot}{}
\newcommand{\roserXInstarcdipsI}{}

\newcommand{\cgXVIIInclustertot}{}
\newcommand{\cgXVIIInclustercdipsI}{}
\newcommand{\gaiaXVIIInclustertot}{}
\newcommand{\gaiaXVIIInclustercdipsI}{}

\newcommand{\kXIIInclustertot}{}
\newcommand{\kXIIInclustercdipsI}{}
\newcommand{\dXIVnclustertot}{}
\newcommand{\dXIVnclustercdipsI}{}
\newcommand{\bellXVIInclustertot}{}
\newcommand{\bellXVIInclustercdipsI}{}
\newcommand{\banyanXIIInclustertot}{}
\newcommand{\banyanXIIInclustercdipsI}{}
\newcommand{\banyanXIInclustertot}{}
\newcommand{\banyanXIInclustercdipsI}{}
\newcommand{\banyanXInclustertot}{}
\newcommand{\banyanXInclustercdipsI}{}
\newcommand{\krausXIVnclustertot}{}
\newcommand{\krausXIVnclustercdipsI}{}
\newcommand{\ohXVIInclustertot}{}
\newcommand{\ohXVIInclustercdipsI}{}
\newcommand{\rizzutoXInclustertot}{}
\newcommand{\rizzutoXInclustercdipsI}{}
\newcommand{\roserXInclustertot}{}
\newcommand{\roserXInclustercdipsI}{}
% END CLUSTER TABLE

@@

\begin{abstract}
  % Context
  The Transiting Exoplanet Survey Satellite (TESS) has started to
  photometrically monitor almost every star cluster in
  the solar neighborhood.
  % Aims
  As part of the CDIPS project, we have been processing the TESS
  full-frame images to make light curves of stars that
  could be members of stellar associations, moving groups, and open clusters.
  %
  Our eventual hope is to discover giant transiting planets, and probe
  the exoplanet size and separation distributions for planets younger
  than 1 Gyr.
  %
  For this study, we made \numberlcs light curves of candidate young
  stars in \numberclusters clusters.
  Each light curve represents between 20 and 25 days of observations
  of a star brighter than $G_{Rp}=16$, sampled at 30 minute cadence.
  % Methods
  We describe in detail the image subtraction and time-series analysis 
  techniques we used to create the light curves, which
  have noise properties in agreement with theoretical expectations.
  % Results
  We then highlight the \numberpcs planet candidates we identified in
  an initial search, describe the vetting procedures that they have
  survived, and emphasize the value that additional
  spectroscopic, photometric, and imaging observations will have in
  verify that these candidates are in fact planets.
  %
  We also comment on the possible use of the light curve sample for
  studies of stellar rotation evolution, and binary eccentricity
  damping.
  %
  The light curves and vetting reports are available at
  \url{archive.stsci.edu/prepds/cdips}.
\end{abstract}

\keywords{
  methods: data analysis ---
  techniques: photometric ---
  %TODO: could be individual, and enumerate each cluster as well.
  (Galaxy:) open clusters and associations: general ---
  planets and satellites: detection 
}

@@

Many evolutionary processes are expected to occur over the lives of
stars and exoplanets; it would be interesting to statistically observe
these changes as functions of time.  However, since most dwarf star
properties do not appreciably change until the stars evolve off the
main sequence, creative approaches must be used to infer stellar ages
\citep{soderblom_ages_2010}.  One approach beginning to bear fruit in
the study of exoplanets is to search for planets in coeval groups of
stars, {\it i.e.} in clusters.  This includes the open clusters of
yore, as well as the moving groups and stellar associations that began
to be uncovered in the late 1990s \citep{zuckerman_young_2004}.  The
ages of these stellar ensembles are inferred through isochrone
analyses on color-magnitude diagrams, using an appropriate combination
main-sequence turnoff locations, pre-MS turnon locations, and/or MS
isochrones for the known cluster members \citep[{\it e.g.},][Section
3.4.3]{kharchenko_global_2012}.  Once calibrated, gyrochronology can
also be used to verify the age of a stellar ensemble \citep[{\it
e.g.},][]{barnes_color-period_2015,meibom_spin-down_2015,curtis_tess_2019}.
The ages of planets discovered in these cluster stars are then
assumed to equal the age of the larger stellar ensemble.

@@

%FIXME probably rework the following two paragraphs?
The TESS mission \citep{ricker_transiting_2015} holds the promise to
deliver the most homogeneous and comprehensive cluster photometric
survey in history.  As an order of magnitude estimate, the 
\citet{Kharchenko_et_al_2013} combined with the TESS apparent magnitude
calculator of \citet{Jaffe_Barclay_2017} indicated that $\approx
2\times10^5$ cluster members brighter than $T=16$ will be observed in
the full-frame images over the first two years of TESS observations.
The actual number will be larger, as cluster membership catalogs
are not yet complete, even at these relatively bright magnitudes
\citep[{\it e.g.},][]{cantat-gaudin_gaia_2018,cantat-gaudin_newOCs_2019}.
% For example, using Gaia-DR2 \citet{cantat-gaudin_newOCs_2019}
% discovered a few tens of previously undetected open clusters in
% the direction of Perseus. Earlier, \citet{cantat-gaudin_gaia_2018}
% fortuitously discovered 60 open clusters as well; however a
% homogeneous all-sky search with Gaia data has yet to be performed.

For moving groups and stellar assocations, it is typically a simple thing to do
aperture photometry.  A number of promising targets from TESS are in various
stages of follow-up for this, notably DS Tuc Ab (TOI 200,
\citealt{benatti_dstuc_2019}, Newton+2019), as well as TOI-450 and TOI-451.
This is good, and these will remain benchmark systems because they are close
and bright.  However, to do statistics, we need more stars -- we need to
investigate the full range of cluster properties (densities, ages,
metallicities).  This motivates the need to go crowded.

One of the major challenges in deriving precise photometry from the
TESS images is the relatively poor angular resolution ($\approx
21''$).  Almost all clusters are within 10 degrees of the Galactic
plane (see FIGURE~1). The problems with crowding and complex
backgrounds are so severe near the galactic plane that the {\it
TESS}\, Candidate Target List has deprioritized all objects at
galactic latitudes less than $\approx
15^\circ$~\citep{stassun_TIC_2018,stassun_TIC8_2019}, which includes
90\% of all star clusters\footnote{TICv8 updates this to $10^\circ$,
but for the first year of TESS observations, the number used when
selecting target stars was $15^\circ$.}.
This is sensible, given that the large pixel size and the high stellar
surface density will make aperture photometry unreliable.  However, it
also means that a large number of stars in clusters that could yield
planet candidates may go unprocessed by the official {\it TESS} data
reduction pipeline.

We have therefore opted to produce time-series photometry from the
TESS images for stars in ``clusters''~--~a collective term we adopt
for open clusters, moving groups, stellar associations, and
star-forming regions.
We are also including some stars that we suspect are young due to
combined photometric and astrometric indicators.
We are using the difference imaging technique because of its benefits
in modelling complex backgrouds in crowded regions.
Our eventual hope is to discover giant transiting planets, and probe
the exoplanet size and separation distributions for planets younger
than 1 Gyr.

%FIXME improve
In what follows, \S~\ref{sec:starselection} describes the process of
selecting stars.  \S~\ref{sec:method} presents the photometric and
image processing methods, and
\S~\ref{sec:results} describes results.
\S~\ref{sec:discussion} discusses, and \S~\ref{sec:conclusion}
concludes.

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.7\textwidth]{cluster_positions.pdf}
	\end{center}
	\vspace{-0.5cm}
	\caption{
    {\bf TESS looks at many clusters.} Placeholder skymap.
		\label{fig:clustermap}
	}
\end{figure*}

\begin{figure}[t]
    \begin{center}
        \leavevmode
        \includegraphics[width=0.49\textwidth]{cluster_field_star_positions.png}
    \end{center}
    \vspace{-0.5cm}
    \caption{
        {\bf Celestial positions of light curves from Sectors 6 and 7.}
        \label{fig:lcradecsector6}
    }
\end{figure}

\begin{figure}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.49\textwidth]{cam1_cluster_field_star_positions.png}
	\end{center}
	\vspace{-0.5cm}
	\caption{
    {\bf Celestial positions of light curves from Sector 6, Camera 1.}
		\label{fig:lcradec}
	}
\end{figure}

@@

We reduced the TESS images to light curves by performing a sequence of
steps using stand-alone programs.
Our overall method is in the spirit of the reduction approaches described
by \citet{Pal_2009}, \citet{soares-furtado_image_2017} and
\citet{oelkers_precision_2018}; a conceptual overview is given in
Figure~\ref{fig:pipeline}.

@@

While we performed numerous initial tests on the first sectors of data,
by geometric coincidence Sectors 1--5 fell away from the galactic plane.
Less than 2\% of the CDIPS target star sample
is therefore observed in the first five TESS sectors.
Though a few interesting clusters are present ({\it e.g.}, Blanco~1, NGC~2516, NGC~1901),
for the time being we opted to focus on sectors in which there were stars
of interest for our intended science.
These begin in Sector 6 (2018-12-12, spacecraft orbit \#19).

@@

The second reference frame is the
photometric reference, which is used both to calculate the
convolution kernel, and to obtain a
reference flux for each star.  
To minimize Poisson errors, our photometric refernce is a median average of
$N=50$ selected frames.
The sub-frames are chosen to have low scatter in their photometry,
and low background measurements, using the metadata collected
in \S~\ref{subsec:preparation}.
We convolve the 50 best candidate photometric references to the best
photometric reference, and then perform a median combination of the
frames to make the photometric reference.

@@

\begin{figure}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.49\textwidth]{rms_vs_mag.png}
	\end{center}
	\vspace{-0.5cm}
  \caption{ {\bf Standard deviation vs catalog TESS-band magnitude for
  trend-filtered CDIPS light curves.} The minimum RMS across all three
  aperture sizes was selected.  The photon and read noise are
  calculated using the effective area from \citet{vanderspek_2018}.
  The noise from unresolved background stars is expected to be more
  important than read noise at the faint end, but is omitted from the
  plot due to model uncertainties (see \S~\ref{subsec:lcstatistics}).
		\label{fig:rms_vs_mag}
	}
\end{figure}

@@

The standard deviation of the light curves is plotted as a function of the 
catalog $T$-band magnitude for CDIPS light curves in 
Figure~\ref{fig:rms_vs_mag}.
Ignoring the expected noise contribution from the zodiacal and faint star 
background, the light curves generally seem to follow the model one would 
predict.
The bright end is somewhat noisier than the performance reported by SPOC 
(CITE), as well as the pipelines of 
Chelsea (CITE) and Ben (CITE), and maybe Ryan (CITE).
Simple aperture photometry should out-perform image subtraction techniques in 
the bright regime, so this is not particularly unexpected.

A few points concerning the noise model predictions are relevant.
First, the effects of crowding are not apparent in 
Figure~\ref{fig:rms_vs_mag}. 
If the reference fluxes were being measured directly from the photometric 
reference frame, the faint stars would be driven below the expected noise 
floor, because the reference fluxes would be systematically overestimated.
Our procedure for determining the reference magnitudes uses our knowledge of 
the catalog magnitudes to eliminate this effect (REFERENCE).

Second, our plot omits the noise from unresolved background stars.
If we include it, then our RMS at the faint end is about 0.7x below the model.
This suggests that the model over-predicts the background, or that we overfit 
the majority of our light curves. Both are probably a little true.

ACF statistics before and after detrending(?)

@@

\paragraph{Light curve provenance}.
In Sector 6, about 49{,}000 light curves of candidate cluster stars
were made. The provenance of the claimed cluster origin of these
sources is \citet{dias_proper_2014} for 59\% of the sources;
\citet{zari_3d_2018} for 16\% of sources from their upper
main-sequence table and 1\% of sources from their PMS table;
\citet{Kharchenko_et_al_2013} for 8\% of sources,
\citet{cantat-gaudin_gaia_2018} for 6\% of sources, and more than two
catalogs for the remaining 10\% of sources.

@@

As an initial search for transiting planets, strong stellar rotators, and 
eclipsing binaries, we performed a few steps of post-processing. For 
simplicity,
we chose a single aperture size~--~``aperture 2''~--~with a radius of 1.5 
pixels, to perform the period search.

First, to identify periodic transit-like signals, we used 
\citet{hippke_TLS_2019}'s transit least-squares (TLS) tool.
The algorithm is the same as the canonical box least-squares
\citep{kovacs_box-fitting_2002}, except in place of a box template, a transit 
template is used  for a marginal improvement of the detection efficiency.
In addition, the search grids in \texttt{tls} 
\footnote{\url{https://github.com/hippke/tls}} are slightly more 
efficient than in most BLS implementations, since \texttt{tls} uses the 
cubic-in-frequency sampling advocated by \citet{ofir_optimizing_2014}, 
rather than standard linear-in-frequency sampling.
During the period search, we rejected $6\,{\rm hours}$ at the
beginning and end of each spacecraft orbit, to mitigate the presence
of correlated red noise in the results.
This shrinks the data volume by about 5\%, but also lowers the number
of systematic false positives in subsequent vetting.
Our grids typically consisted of about 30 different durations, and
about 5000 periods between 0.5 and 21 days. 
We also ran a generalized Lomb-Scargle periodogram (CITE), simply to 
have additional periodicity information.

We then performed a cut on the TLS signal detection efficiency:
${\rm SDE} > 12$.
This yielded XXX light curves, and we then
performed TFA signal reconstruction on these lightcurves using 
\texttt{vartools}.
In this process, the model lightcurve $A(i)$ in 
Equation~\ref{eq:tfa_to_minimize} is set to the phase-binned signal from the 
most powerful peak in the TLS spectrum, rather than being a constant function. 
Generally speaking, this helps improve the quality of the resulting light 
curve.

We then make a multi-page \texttt{.pdf} document with the information 
necessary to make classifications for vetting.
These documents are released along with the light curves, as a useful summary
 for anyone interested in the subset of objects that we have analyzed.
A full description of each page of the summary \texttt{.pdf} is given in the 
Appendix.

>>>>

% BEGIN NUMBERS
\newcommand{\numberpcs}{42\ }
\newcommand{\sVInumberlcs}{67{,}601\ }  % 2019/06/20 not allnan
\newcommand{\sVIInumberlcs}{91{,}736\ }  % 2019/06/20 not allnan
\newcommand{\numberlcs}{159{,}337\ } % 2019/06/20 sum
\newcommand{\numberclusters}{XXX\ }

@@

\begin{abstract}
  % Context
  The Transiting Exoplanet Survey Satellite (TESS) has begun to
  photometrically monitor almost every star cluster in
  the solar neighborhood.
  % Aims
  The CDIPS project is processing the TESS
  full-frame images and making light curves of stars that could be
  members of stellar associations, moving groups, or open clusters.
  %
  Our eventual hope is to discover giant transiting planets with known
  ages, and probe the exoplanet size and separation distributions for
  planets younger than 1 Gyr.
  %
  In this study, we made \numberlcs light curves of candidate young
  stars in \numberclusters clusters.
  Each light curve represents between 20 and 25 days of observations
  of a star brighter than $G_{Rp}=16$, sampled at 30 minute cadence.
  % Methods
  We describe in detail the image subtraction and time-series analysis 
  techniques we used to create the light curves, which
  have noise properties in agreement with theoretical expectations.
  % Results
  We then highlight the \numberpcs planet candidates we identified in
  an initial search, describe the vetting procedures that they have
  survived, and emphasize the additional spectroscopic, photometric,
  and imaging observations that are needed to verify that these
  candidates are in fact planets.
  %
  We also comment on the possible use of the light curve sample for
  studies of stellar rotation evolution, and binary eccentricity
  damping.
  %
  The light curves and vetting reports are available at
  \url{archive.stsci.edu/prepds/cdips}.
\end{abstract}

\keywords{
  planets and satellites: detection  --
  methods: data analysis ---
  techniques: photometric ---
  (Galaxy:) open clusters and associations: general ---
}

@@

Many evolutionary processes are expected to occur over the lives of
stars and exoplanets; it would be interesting to statistically observe
these changes as functions of time.  However, since most dwarf star
properties do not appreciably change until the stars evolve off the
main sequence, creative approaches must be used to infer stellar ages
\citep{soderblom_ages_2010}.  One approach beginning to bear fruit in
exoplanet studies is to search for planets in coeval groups of stars,
hereafter ``clusters''.  This includes the open clusters of yore, as
well as the moving groups and stellar associations that began to be
uncovered in the late 1990s \citep{zuckerman_young_2004}.  The ages of
these stellar ensembles are inferred through isochrone analyses of
color-magnitude diagrams, using an appropriate combination of
main-sequence turnoff locations, pre-main-sequence turnon locations,
and possibly averaged MS isochronal ages across known cluster members
\citep[{\it e.g.},][Section 3.4.3]{kharchenko_global_2012}.  Once
calibrated, gyrochronology can also be used to verify the age of a
stellar ensemble \citep[{\it
e.g.},][]{barnes_color-period_2015,meibom_spin-down_2015,curtis_tess_2019}.
The ages of planets discovered in these cluster stars are then assumed
to equal the age of the larger stellar ensemble.

@@

The TESS mission \citep{ricker_transiting_2015}, though designed for
other purposes, holds the promise to deliver the most homogeneous and
comprehensive cluster photometric survey in history.  More
quantitatively, the \citet{Kharchenko_et_al_2013} cluster member
database indicates that $\approx 2\times10^5$ open cluster members
brighter than $T=16$ will be observed in the full-frame images over
the first two years of TESS observations.  The actual number will be
larger, as cluster membership catalogs are not yet complete, even at
these relatively bright magnitudes \citep[{\it
e.g.},][]{cantat-gaudin_gaia_2018,cantat-gaudin_newOCs_2019}.
% Our target list currently sits at $\approx 1.0\times10^6$ candidate
% young stars, perhaps one-third of which are bonafide cluster members
% (see \S~\ref{sec:starselection}).

One of the major challenges in deriving precise photometry from the
TESS images is the relatively poor angular resolution ($\approx 21''$
per pixel).  Almost all clusters are within 10 degrees of the Galactic
plane. The problems with crowding and complex backgrounds are so
severe near the galactic plane that the TESS Candidate Target List has
deprioritized all objects at galactic latitudes less than $\approx
15^\circ$~\citep{stassun_TIC_2018,stassun_TIC8_2019}, which includes
90\% of all star clusters\footnote{TICv8 has updated this to $10^\circ$,
but for the first year of TESS observations, the number used when
selecting target stars was $15^\circ$.}.  This is sensible, given that
the large pixel size and the high stellar surface density will make
aperture photometry unreliable.  However, it also means that a large
number of stars in clusters that could yield planet candidates may go
unprocessed by the official {\it TESS} data reduction pipeline.

If one's concern is to discover and characterize benchmark systems
with known ages,
hunting for transiting planets in nearby stellar assocations is a path
that seems to be working.  A number of promising targets from TESS are
in various stages of follow-up from this approach, notably DS Tuc Ab
(TOI 200, \citealt{benatti_dstuc_2019}, Newton+2019), as well as
TOI-450 and TOI-451.  This is good, and these will remain benchmark
systems because they are close and bright.  However, to do statistics,
we need more stars -- we might also benefit from investigating the full range of cluster
properties (densities, ages, metallicities).  This motivates the need
to go crowded, and fainter.

We have therefore opted to produce time-series photometry from the
TESS images of any star that could be a member of a coeval group.  We
are also including some stars that we suspect are young due to
combined photometric and astrometric indicators.  We are using the
difference imaging technique because of its benefits in modelling
complex backgrouds in crowded regions.  While we hope to
discover at least a few giant transiting planets, a separate hope
is that the dataset might be useful to those wishing to study the
time evolution of stellar processes.

In the following, \S~\ref{sec:starselection} describes the process of
selecting target stars.  \S~\ref{sec:method} presents the photometric and
image processing methods, and \S~\ref{sec:results} describes results.
\S~\ref{sec:discussion} discusses, and \S~\ref{sec:conclusion}
concludes.

%\begin{figure*}[t]
%	\begin{center}
%		\leavevmode
%		\includegraphics[width=0.7\textwidth]{cluster_positions.pdf}
%	\end{center}
%	\vspace{-0.5cm}
%	\caption{
%    {\bf TESS looks at many clusters.} Placeholder skymap.
%		\label{fig:clustermap}
%	}
%\end{figure*}

\begin{figure*}[!ht]
    \gridline{
      \fig{cluster_field_star_positions.png}{0.49\textwidth}{}
      \fig{cam1_cluster_field_star_positions.png}{0.49\textwidth}{}
    }
    %\begin{center}
    %    \leavevmode
    %    \includegraphics[width=0.49\textwidth]{cluster_field_star_positions.png}
    %\end{center}
    \vspace{-0.5cm}
    \caption{
        {\it Left}. Celestial positions of light curves from Sectors 6 and 7.
        {\it Right}. Celestial positions of light curves from Sector 6, Camera 1.
        \label{fig:lcradecsector6}
    }
\end{figure*}

% \begin{figure}[t]
% 	\begin{center}
% 		\leavevmode
% 		\includegraphics[width=0.49\textwidth]{cam1_cluster_field_star_positions.png}
% 	\end{center}
% 	\vspace{-0.5cm}
% 	\caption{
%     {\bf Celestial positions of light curves from Sector 6, Camera 1.}
% 		\label{fig:lcradec}
% 	}
% \end{figure}

@@

We reduced the TESS images to light curves by performing a sequence of
steps using stand-alone programs.
Our overall method is in the spirit of the reduction approaches described
by \citet{Pal_2009}, \citet{huang_high-precision_2015}, \citet{soares-furtado_image_2017} and
\citet{oelkers_precision_2018}; a conceptual overview is given in
Figure~\ref{fig:pipeline}.

@@

While we performed numerous initial tests on the first sectors of data,
by geometric coincidence Sectors 1--5 were pointed away from the galactic plane.
Less than 2\% of the CDIPS target star sample
was therefore observed in the first five TESS sectors.
Though a few interesting clusters are present ({\it e.g.}, Blanco~1, NGC~2516, NGC~1901),
for the time being we opted to focus on sectors in which there were stars
of interest for our intended science.
These begin in Sector 6 (2018-12-12, spacecraft orbit \#19).
For this run of processing, they conclude at the end of Sector 7
(2019-02-01, spacecraft orbit \#22).

@@

The second reference frame is the
photometric reference, which is used both to calculate the
convolution kernel, and to obtain a
reference flux for each star.  
To minimize Poisson errors, our photometric reference is a median average of
$N=50$ selected frames.
The sub-frames are chosen to have low scatter in their photometry,
and low background measurements, using the metadata collected
in \S~\ref{subsec:preparation}.
We convolve the 50 best candidate photometric references to the best
photometric reference, and then perform a median combination of the
frames to make the photometric reference.

@@

\subsubsection{Stellar properties}

@@

Describe
Figure~\ref{fig:cdf_T_mag}
Figure~\ref{fig:hrd}
Figure~\ref{fig:propermotions}

\subsubsection{Cluster membership provenance}.

\paragraph{Sector 6}
In Sector 6, \sVInumberlcs light curves of candidate cluster stars
were made. The provenance of the claimed cluster origin of these
sources is \citet{dias_proper_2014} for 59\% of the sources;
\citet{zari_3d_2018} for 16\% of sources from their upper
main-sequence table and 1\% of sources from their PMS table;
\citet{Kharchenko_et_al_2013} for 8\% of sources,
\citet{cantat-gaudin_gaia_2018} for 6\% of sources, and more than two
catalogs for the remaining 10\% of sources.

\paragraph{Sector 7}
In Sector 7, \sVIInumberlcs light curves of candidate cluster stars
were made. The provenance of the claimed cluster origin of these
sources is  ...

The clusters with the largest claimed numbers of sources are ...

\subsubsection{Light curve noise properties}

\begin{figure}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.49\textwidth]{rms_vs_mag.png}
	\end{center}
	\vspace{-0.5cm}
  \caption{ {\bf Standard deviation vs catalog TESS-band magnitude for
  trend-filtered CDIPS light curves.} 
  The minimum RMS across all three
  aperture sizes was selected.  The photon and read noise are
  calculated using the effective area from \citet{vanderspek_2018}.
  The noise from unresolved background stars is a function of
  galactic latitude, and dominates over zodiacal light and read noise
  for faint stars near the galactic plane; the dotted line assumes a
  sight-line towards the center of Sector 6, Camera 1 (further details
  are in \S~\ref{subsec:lcstatistics}).
		\label{fig:rms_vs_mag}
	}
\end{figure}

\paragraph{Observed RMS vs magnitude.}
The standard deviation of the TFA-detrended light curves is plotted as
a function of the catalog $T$-band magnitude for CDIPS light curves in
Figure~\ref{fig:rms_vs_mag}.
For the $y$-axis of this plot, we have taken
\begin{equation}
  {\rm RMS} = \left[
    \frac{1}{N-M-1}
    \sum_{i=1}^{N} (f_i - \bar{f})^2
  \right]^{1/2},
\end{equation}
where $f_i$ is the value of the flux at the $i^{\rm th}$ point in the
time-series, $\bar{f}$ is the mean flux, $N$ is the
number of points in the time-series, and $M$ is the number
of template light curves used during TFA detrending.
The correction in the denominator penalizes the natural degree of
overfitting inherent to the TFA algorithm.

The observed RMS (black points) follows the expected shape,
with photon noise dominating from $T=9$ to $T=12$, beyond which the
onset of the ``sky'' background changes the overall slope of the
curve to a slightly steeper scaling.
For the brightest stars ($T\lesssim 9$), a ``systematic floor'' was an
expected part of the mission's error budget \citep{ricker_transiting_2015}, 
but 
has not been observed in early
reports of the photometric performance of various aperture photometry
pipelines ({\it e.g.,} the SPOC pipeline \citealt{jenkins_spoc_2010},
the MIT-QLP \citealt{huang_tess_2018}, and \texttt{eleanor}
\citealt{feinstein_eleanor_2019}).
The fact that our light curves for the brightests stars are above this
purported ``floor'', rather than below it, suggests that our
image subtraction techniques could be introducing some small degree of
noise to the light curves of the brightest stars.
It is also true however that our largest aperture contains only about
16 pixels, which is sub-optimal for stars brighter than $T\approx9$
\citep[see][Figure~14]{Sullivan_et_al_2015}.
Since the brightest stars are not the focus of the present work, we
leave this as a point to improve in future work.

Importantly, the faint stars do not noticeably exhibit
the typical effects of crowding at the faint end 
\citep[{\it e.g.},][Figure~5]{feinstein_eleanor_2019}.
In aperture photometry pipelines, star in very crowded regions typically 
have their flux overestimated relative to what would be predicted from their
catalog magnitudes.
This leads to systematic underestimates of the uncertainty in the relative 
fluxes, as well as ``flux contamination'' (the reduction in amplitude of say, 
transit signals, due to diluting flux).
Our method to work around this problem -- using the catalog magnitudes to 
predict the reference flux values, and measuring deviations from these 
reference fluxes on the subtracted images -- seems to be performing as we had 
hoped.

\paragraph{Expected RMS vs magnitude.}

The noise model shown in Figure~\ref{fig:rms_vs_mag} is quite similar
to that of \citet{Sullivan_et_al_2015}, save for two changes.
The first change is minor: the effective area of the telescope is
updated to be $86.6\,{\rm cm}^2$, per the measurements of
\citet{vanderspek_2018}.

The second point is more important: we explicitly include the
estimated noise contribution from unresolved faint stars.  The
brightness of the diffuse sky is dominated by different sources at
different wavelengths.  For instance, the CMB is most important in
the microwave, and thermal radiation from dust grains in the solar
system (zodiacal light) is dominant in the far infra-red
\citep{leinert_1997_1998}.  In the TESS-band, both zodiacal light and
faint stars can play a role, depending on the line of sight under
consideration. The zodiacal light is brightest near the ecliptic
plane, and the faint star background is brightest near the galactic
plane (and towards the galactic center).  \citet{winn_background_2013}
estimated the photon-counts from each component that would be observed 
by TESS.
His zodiacal light model was presented by \citet{Sullivan_et_al_2015},
but the faint star model was not emphasized since the Sullivan
simulations were performed away from the galactic plane.

A few words are therefore pertinent about the diffuse sky model we
have used for Figure~\ref{fig:rms_vs_mag}, which is adopted explicitly
because most of our target stars are near the galactic plane.
Stars are judged to be ``unresolved'' and part of the background if
their surface density exceeds the angular resolution of the telescope.
TESS has an angular resolution of $\Delta \theta \sim 1'$, set by a
combination of the pixel size as well as the typical stellar FWHM.
Sources with sky surface density exceeding $\Delta \theta^{-2}$
therefore contribute to the background.

The relevant quantity needed to calculate the integrated 
photon counts from faint sources
is  $N(<m,l,b)$ --- the number of stars per square arcsecond
brighter than magnitude $m$, along a line of sight with galactic
longitude and latitude $(l,b)$.
\citet{winn_background_2013} queried the Besan\c con model 
\citep{robin_synthetic_2003}  along a grid of galactic sight-lines, and 
converted the resulting $N(<m,l,b)$ surface densities into $I$-band surface 
brightnesses.
Fitting a smooth function to the results, \citet{winn_background_2013} found
\begin{equation}
I\ {\rm mag\ arcsec}^{-2} =
    a_0 + a_1 \left(\frac{|b|}{40^\circ}\right)
    + a_2 \left(\frac{|l|}{180^\circ}\right)^{a_3},
\end{equation}
where the galactic longitude $l$ is measured from $-180^\circ$ to 
$180^\circ$, and the empirical coefficients were found to be $a_0 = 18.9733$, 
$a_1=8.833$, $a_2=4.007$, and $a_3=0.805$.
This fit was cautioned to be {\it very approximate}.
It is sensitive to the threshold used to select ``unresolved'' stars, and 
likely no more accurate than 0.5 mag on average.
In regions with exceptionally high extinction ({\it e.g.}, star forming 
regions) it is expected to systematic underestimate the background brightness 
by an even larger degree.

\paragraph{ACF statistics}
ACF statistics before and after detrending(?)

@@

@@

To identify an initial set of transiting planets, strong stellar rotators, and 
eclipsing binaries, we performed a few steps of post-processing on the light 
curve described in the preceding sections. 
This processing was entirely independent of the data release, since it was 
quite specific to our own scientific interests.

For simplicity,
we first chose a single aperture size~--~``aperture 2''~--~with a radius of 
1.5  pixels.
Then, to identify periodic transit-like signals, we used 
\citet{hippke_TLS_2019}'s transit least-squares (TLS) tool.
The algorithm is the same as the canonical box least-squares
\citep{kovacs_box-fitting_2002}, except in place of a box template, a transit 
template is used  for a marginal improvement of the detection efficiency.
In addition, the search grids in \texttt{tls} 
\footnote{\url{https://github.com/hippke/tls}} are slightly more 
efficient than in most BLS implementations, since \texttt{tls} uses the 
cubic-in-frequency sampling advocated by \citet{ofir_optimizing_2014}, 
rather than standard linear-in-frequency sampling.
Our grids typically consisted of about 30 different durations, and
about 5000 periods between 0.5 and 21 days.

Before performing the period search, we rejected $6\,{\rm hours}$ at the
beginning and end of each spacecraft orbit, to mitigate the presence
of correlated red noise in the results.
This shrank the data volume by about 5\%, but also lowered the number
of systematic false positives in subsequent vetting.
We then performed an asymmetric sigma-clipping of $(50\sigma,5\sigma)$ to 
preserve transits while omitting flares and other positive flux excursions.

A number of the light curves show residual variability, often of stellar 
origin.
This expected for a sample of young stars; the issue of finding transits in 
the face of large stellar rotation signals 
has been explored by both \citet{rizzuto_zeitV_2017} and also 
\citet{hippke_wotan_2019}.
The former adopted an approach that we have yet to explore, which is to 
pass a sliding window over the light curve that, within each step, performs a 
Bayesian model comparison between a spline and a spline-plus-notch model.  If 
the spline-plus-notch model is favored, the transits are preserved for 
subsequent discovery.
\citet{hippke_wotan_2019}, conversely, described a large number of possible 
detrending methods, and found that many performed more or less the same at 
recovering planetary transits for a sample of young stars with strong rotation 
signals.

Our approach in this work is essentially identical to one of the methods 
described by \citet{hippke_wotan_2019}.
First, we run a generalized Lomb-Scargle periodogram (CITE) on each TFA light 
curve.
If a peak is found with false alarm probability below $10^{-5}$, we consider 
the star ``variable'', and opt to 
detrend the light curve with robust penalized B-splines, which are splines 
with knot-length automatically determined via cross-validation 
\citep{eilers_flexible_1996}. The idea behind the cross-validation is that a 
larger  number of knots leads to smaller residuals on training data, but 
larger errors 
when tested on the entire dataset.
We used the \texttt{wotan} implementation, which is a wrapper to the 
\texttt{pyGAM} spline fitter, with $2\sigma$ clipping of outliers from the fit 
residuals at each iteration 
\citep{serven_pygam_2018_1476122,hippke_wotan_2019}.
The maximum number of spline knots is set to 50, which for each TESS sector 
($\approx 25\,{\rm days}$) is commensurate with a $\approx0.5\,{\rm day}$ 
window.

\begin{figure}[!ht]
    \gridline{\fig{tlsresult_sector6.png}{0.45\textwidth}{}}
    \vspace{-0.8cm}
    \gridline{\fig{tlsresult_sector7.png}{0.45\textwidth}{}}
    \caption{
        Significance thresholds empirically defined for the transiting planet 
        search described in \S~\ref{subsec:ctois}. Each point represents the 
        TLS periodogram peak signal detection efficiency from one light curve.
        {\it Top.} Sector 6.  {\it Bottom.} Sector 7.
    }
    \label{fig:tlsresults}
\end{figure}

After (optionally) detrending, we run the TLS search. To select 
``significant'' signals for visual inspection, we 
performed a cut on the TLS signal detection efficiency defined piecewise over 
the signal periods.
The overall lower limit is ${\rm SDE} > 12$, with higher limits imposed in 
regions with heavy contamination from systematic signals.
The signals for sectors 6 and 7 are shown in the space of SDE vs period in 
Figure~\ref{fig:tlsresults}.

This yielded a few thousand light curves.  About two-thirds already had been 
detrended with splines, and were not processed further.
For the remaining third we
performed TFA signal reconstruction using 
\texttt{vartools}.
In this process, the model lightcurve $A(i)$ in 
Equation~\ref{eq:tfa_to_minimize} is set to the phase-binned signal from the 
most powerful peak in the TLS spectrum, rather than being a constant function. 
This helps improve lower the scatter of the light curve at frequencies near 
the TLS peak.
